\documentclass{beamer}

\usepackage{graphicx}
\usepackage{color}
\usepackage{listings}
\usepackage{parskip}
\usepackage{textcomp}

\frenchspacing

\definecolor{commentcolor}{rgb}{0, 0.7, 0.3}
\definecolor{keywordcolor}{rgb}{0.6, 0, 0.5}
\definecolor{stringcolor}{rgb}{0, 0, 0.9}

\lstset {%
	language=[LaTeX]TeX,
	basicstyle=\ttfamily,
	breaklines=true,
	numbers=left,
	tabsize=4,
	commentstyle=\color{commentcolor},
	keywordstyle=\color{keywordcolor},
	stringstyle=\color{stringcolor},
	columns=flexible,
}

\title{Introduction to \LaTeX{}}
\subtitle{A \LaTeX{} Presentation}
\author{Vincent Macri\\JJ Marr}
\date{2017}

\usecolortheme{beaver}
\beamertemplatenavigationsymbolsempty
\usefonttheme[onlymath]{serif}
\logo{\rmfamily\normalsize\LaTeX{}}

\AtBeginSection[] {%
	\begin{frame}
	\frametitle{Lesson Progress}
	\tableofcontents[currentsection]
	\end{frame}
}

\begin{document}
	\frame{\titlepage}
	\section{Introduction}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Welcome to \LaTeX{}}
		\begin{itemize}[<+->]
			\item Lamport \TeX{}
			\item Written as \LaTeX{} or LaTeX.
			\item Pronounced lay-tek
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Why we use \LaTeX{}}
		\LaTeX{} is a very useful skill if you plan on doing:
		\pause
		\begin{itemize}
			\item Math
			\item Computer science
			\item Engineering
			\item Physics
			\item Chemistry
			\item Publishing
		\end{itemize}
		\pause
		Since \LaTeX{} is so versatile, once you get used to it, you will find that you can do almost anything in it.
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Learning \LaTeX{}}
		The hardest part about learning \LaTeX{} is getting started.
		\pause

		So congratulations! You're done the hard part!
		\pause

		When using \LaTeX{}, it is important to remember that it makes correct design choices 99\% of the time. Accept what it does, as it does it for a reason.
		\pause

		For example, \LaTeX{} uses very large margins by default. It may look odd, but it actually sets the margins to make lines the size that studies have shown is best for readability (60--70 characters). This is easy to change of course.
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Basic syntax}
		\begin{description}[<+->]
			\item[Spacing] Spaces in \LaTeX{} don't do much. \LaTeX{} treats 20 spaces the same as it treats 1 space.
			\item[Inline math] \lstinline{\$1 + 2 = 3\$} $\rightarrow 1 + 2 = 3$ In math mode, you can use 0 or 20 spaces, \LaTeX{} will output the same thing. Do whatever you find easiest to write and edit.
			\item[Comments] Comment \LaTeX{} code with the \% symbol. Write \textbackslash\% to use the \% symbol.
			\item[Commands] \LaTeX{} uses commands to perform quick actions. They are formatted as \textbackslash command\{parameter\}. For some commands, the \{\} and parameter are optional.
			\item[Environments] \LaTeX{} uses environments for things more advanced than commands. They start with \textbackslash begin\{environment\} and end with \textbackslash end\{environment\}
		\end{description}
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Installing}
		Installing \LaTeX{} is easy, but there are lots of options for installing it.
		
		Listed below are the easiest solutions for the main desktop operating systems. Some of these work on all operating systems, but certain ones are easier with certain operating systems.
		\begin{description}
			\item[Any Good OS (GNU/Linux, BSD, etc.)] Install \TeX{} Live from your distro's repo.
			\item[macOS] Who knows. There are online editors
			\item[Windows] MikTeX is a GUI program for editing and compiling \LaTeX{}
		\end{description}
		If you have difficulty installing \LaTeX{}, you can try an online editor such as overleaf.com

		You can also check https://www.latex-project.org/get/ if you are not satisfied with any of these options.
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Let's start}
		In this presentation, we will show how to write a \LaTeX{} document that proves the quadratic formula.
	\end{frame}
	\section{Preamble}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{The beginning}
		Our document is split into two sections.

		The \alert{preamble} and the \alert{main document}.
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{The preamble}
		Your preamble is where you tell \LaTeX{} about what is going to be in your document.

		Information is the preamble includes information such as:
		\begin{itemize}[<+->]
			\item Document class
			\item Packages
			\item Document title
			\item Author
			\item Date (defaults to date when document was compiled)
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Example}
		Let's code our preamble.
		\lstinputlisting[linerange=1-9]{QuadraticProof.tex}
	\end{frame}
	\section{Setup}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Your first class}
		\LaTeX{} has different classes for different types of documents.

		We will be using the \lstinline{article} class.
		The \lstinline{article} class is:
		\pause
		\begin{itemize}[<+->]
			\item Common
			\item Simple
			\item Versatile
		\end{itemize}
	\end{frame}
	\begin{frame}[fragile]
	\frametitle{secname}
	\end{frame}
	\begin{frame}
		\frametitle{\secname}
		\framesubtitle{Example}
	\end{frame}
\end{document}
